Missing links, forbidden links, and the topological robustness of food webs

### 2022-07-06 manuscript/ms_C3_v2.tex

Simulation of primary species loss has been conducted in observed food
webs and model food webs from terrestrial and aquatic ecosystems where
robustness was measured in terms of secondary extinctions (Jennifer A.
Dunne, Williams, and Martinez 2002b; Jennifer A. Dunne and Williams
2009). These studies showed that the robustness \textbf{of the food
webs} increases with food web connectance. Also, the removal of the most
connected species cause considerably more secondary extinctions than
random removals of species (Jennifer A. Dunne, Williams, and Martinez
2002a; Sol'e and Montoya 2001). These studies provide an alternate
solution to investigate the impact of primary extinctions in a food web
when canonical experiments in natural ecosystems are not possible.

@@

@@

\caption{\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary **removals of the most connected species** for 12 food webs. S denotes the number of species in a food web. The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary **removals of random species** for 12 food webs. S denotes the number of species in a food web. The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-3}
\end{figure}

@@

{\centering \includegraphics[width=400px]{../results/plot_robustness_all_uncertainty}

@@

>>>>

Simulation of primary species loss has been conducted in observed food
webs and model food webs from terrestrial and aquatic ecosystems where
robustness was measured in terms of secondary extinctions (Jennifer A.
Dunne, Williams, and Martinez 2002b; Jennifer A. Dunne and Williams
2009). These studies showed that the robustness of the food webs
increases with food web connectance. Also, the removal of the most
connected species cause considerably more secondary extinctions than
random removals of species (Jennifer A. Dunne, Williams, and Martinez
2002a; Sol'e and Montoya 2001). These studies provide an alternate
solution to investigate the impact of primary extinctions in a food web
when canonical experiments in natural ecosystems are not possible.

@@

\hypertarget{model-parameterisation-using-approximate-bayesian-computation}{%
\subsection{Model parameterisation using approximate Bayesian
computation}\label{model-parameterisation-using-approximate-bayesian-computation}}

The ADBM was parameterised using approximate Bayesian computation (ABC)
where a set of parameter values were sampled from the prior
distributions. That set of parameter values parameter values were either
accepted and or rejected based on close the predicted is to the observed
food web using a accuracy metric -- True skill statistic. The accepted
parameter values formed a posterior distribution. Further prediction
intervals of the true skill statistic and connectance of the predicted
food webs were calculated. In our study, we considered food webs where
the predicted connectance lies in the 95\% prediction interval of the
predicted connectance.

@@

\caption{\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary removals of the most connected species** for 12 food webs. S denotes the number of species in a food web. The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary \textbf{removals of random species} for 12 food webs. S denotes the number of species in a food web. The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-3}
\end{figure}

@@

{\centering \includegraphics[width=450px]{../results/plot_R50_ADBM_vs_obs}

@@

{\centering \includegraphics[width=450px]{../results/plot_R50_slope}

\caption{\label{fig:fig_r5} Effect size (i.e ratio of relative difference in robustness between ADBM predicted food webs and observed food webs to relative difference in their connectance) shown for the 12 food webs. Red filled circles represent means. Box represent 25th and 75th percentile; black bold midline represent median; whisker represent outlier limits.}\label{fig:unnamed-chunk-6}
\end{figure}
